---
title: "Network Analysis on Game of Thrones"
output: html_notebook
---

In this article, I will be exploring and doing network analysis of the families of major characters from Game of Thrones which is a very famous TV series.

If you are a big Game of thrones fan then you should know that surprisingly, __House Stark__ (specifically Ned and Sansa) and __House Lannister__ (especially Tyrion) are the most important family connections in Game of Thrones; they also connect many of the storylines and are central parts of the Series.


##What is a Network ?

A network in this context is a graph of interconnected nodes/vertices. Nodes can e.g. be people in a social network, genes in a co-expression network, etc. Nodes are connected via edges.


##What can network analysis tell us?


Network analysis can e.g. be used to explore relationships in social or professional networks. In such cases, we would typically ask questions like:

1)How many connections does each person have?

2)Who is the most connected (i.e."famous","Dominating","influential" or 
“important”) person?

3)Are there clusters of tightly connected people?

4)Are there a few key objects that connect clusters of people?
etc.

The answers can give us a lots of information and insights of lots of things and how people interact.


-----------------------



##Implementing It in R





Loading the Required Packages

```{r,warning=FALSE,message=FALSE}

require(tidyverse)
require(ggthemes)
require(igraph)
require(statnet)
```



Now loading the Game of Thrones Datasets

```{r}
#Loading the Datasets
battle<-read.csv("battles.csv")

#Deaths on characters Dataset
deaths<-read.csv("character-deaths.csv")

#pred dataset
pred<-read.csv("character-pred.csv")

```


###Data Preprocessing and Transformation


```{r}
pred[pred == ""] <- NA
#Converting Individual columns to Character data type
pred$name <- as.character(pred$name)
pred$house <- as.character(pred$house)
pred$mother <- as.character(pred$mother)
pred$father <- as.character(pred$father)
pred$spouse <- as.character(pred$spouse)


pred$house <- ifelse(is.na(pred$house) & grepl("Targaryen", pred$name), "House Targaryen", pred$house)
pred$house <- ifelse(is.na(pred$house) & grepl("Stark", pred$name), "House Stark", pred$house)

#gsub() to perform replacement and pattern matching
pred$name <- gsub("[[:punct:]]", "", pred$name)

```


####Creating a new Child_of Dataframe which will contain the Parents and the child's name.


```{r}
child_of <- data.frame(name = pred$name[grepl("son of | daughter of", pred$name)],
                     stringsAsFactors = FALSE)

child_of$child_of <- ifelse(grepl("daughter", child_of$name), paste(gsub("(.* daughter of )(.*)", "\\2", child_of$name), 
  gsub("(.* )(.*)( daughter of.*)", "\\2", child_of$name)), paste(gsub("(.* son of )(.*)", "\\2", child_of$name), 
  gsub("(.* )(.*)( son of.*)", "\\2", child_of$name)))

child_of[child_of$name == "Ulf son of Umar", "child_of"] <- "Umar"

```




Performing a Left Join between the Child_of and Pred Datasets for joining both the tables Together i.e Merging them together with a similar column.
It is similar to using *__'merge()'__* function in R

```{r}
#Joining the 2 tables by common "name" column
pred<-left_join(pred, child_of, by = "name")



#Now I am manually adding the Mother and Father names for the given  children Names
#Inside the brackets the first argument is the condition and second is the the name of the column for which you want to add value
pred[pred$name == "Arya Stark", "mother"] <- "Catelyn Stark"
pred[pred$name == "Arya Stark", "father"] <- "Eddard Stark"

pred[pred$name == "Bran Stark", "mother"] <- "Catelyn Stark"
pred[pred$name == "Bran Stark", "father"] <- "Eddard Stark"

pred[pred$name == "Sansa Stark", "mother"] <- "Catelyn Stark"
pred[pred$name == "Sansa Stark", "father"] <- "Eddard Stark"

pred[pred$name == "Rickon Stark", "mother"] <- "Catelyn Stark"
pred[pred$name == "Rickon Stark", "father"] <- "Eddard Stark"

pred[pred$name == "Jon Snow", "mother"] <- "Lyanna Stark"
pred[pred$name == "Jon Snow", "father"] <- "Eddard Stark"
pred[pred$name == "Jon Snow", "child_of"] <- "Rhaegar Targaryen"

pred[pred$name == "Theon Greyjoy", "mother"] <- "Alannys Harlaw"
pred[pred$name == "Theon Greyjoy", "father"] <- "Balon Greyjoy"

pred[pred$name == "Asha Greyjoy", "mother"] <- "Alannys Harlaw"
pred[pred$name == "Asha Greyjoy", "father"] <- "Balon Greyjoy"

pred[pred$name == "Tommen Baratheon", "house"] <- "House Baratheon/Lannister"
pred[pred$name == "Balon Greyjoy", "house"] <- "House Greyjoy"

pred[pred$name == "Balon Greyjoy", "mother"] <- "Lady of House Sunderly"

pred[pred$name == "Victarion Greyjoy", "mother"] <- "Lady of House Sunderly"
pred[pred$name == "Victarion Greyjoy", "father"] <- "Quellon Greyjoy"

pred[pred$name == "Ramsay Snow", "father"] <- "Roose Bolton"

pred[pred$name == "Myrcella Baratheon", "mother"] <- "Cersei Lannister"
pred[pred$name == "Myrcella Baratheon", "father"] <- "Robert Baratheon"

pred[pred$name == "Shireen Baratheon", "mother"] <- "Selyse Florent"
pred[pred$name == "Shireen Baratheon", "father"] <- "Stannis Baratheon"

pred[pred$name == "Renly Baratheon", "mother"] <- "Cassana Baratheon"
pred[pred$name == "Renly Baratheon", "father"] <- "Steffon Baratheon"

pred[pred$name == "Stannis Baratheon", "mother"] <- "Cassana Baratheon"

#adding a row to the Pred dataset
add <- pred[1, ] #Adding a row
add[1, ] <- NA
add$name <- "Robert Baratheon"
add$mother <- "Cassana Baratheon"
add$father <- "Steffon Baratheon"
add$spouse <- "Cersei Lannister"
pred <- rbind(pred, add) #Binding Row wise to the dataset
 
#----------
  
#Adding some more values

pred[pred$name == "Catelyn Stark", "mother"] <- "Minisa Whent"
pred[pred$name == "Catelyn Stark", "father"] <- "Hoster Tully"

pred[pred$name == "Edmure Tully", "mother"] <- "Minisa Whent"
pred[pred$name == "Edmure Tully", "father"] <- "Hoster Tully"

pred[pred$name == "Lysa Arryn", "mother"] <- "Minisa Whent"
pred[pred$name == "Lysa Arryn", "father"] <- "Hoster Tully"

pred[pred$name == "Robert Arryn", "mother"] <- "Lysa Arryn"
pred[pred$name == "Robert Arryn", "father"] <- "Jon Arryn"

pred[pred$name == "Lyanna Stark", "father"] <- "Rickard Stark"
pred[pred$name == "Eddard Stark", "father"] <- "Rickard Stark"
pred[pred$name == "Brandon Stark", "father"] <- "Rickard Stark"
pred[pred$name == "Benjen Stark", "father"] <- "Rickard Stark"

pred[pred$name == "Rickard Stark", "mother"] <- "Marna Locke"
pred[pred$name == "Rickard Stark", "father"] <- "Edwyle Stark"

pred[pred$name == "Willam Stark", "mother"] <- "Lorra Royce"
pred[pred$name == "Willam Stark", "father"] <- "Beron Stark"

pred[pred$name == "predrik Stark son of Beron", "mother"] <- "Lorra Royce"
pred[pred$name == "predrik Stark son of Beron", "father"] <- "Beron Stark"
pred[pred$name == "predrik Stark son of Beron", "child_of"] <- NA

add <- pred[1, ]
add[1, ] <- NA
add$name <- "Lyarra Stark"
add$mother <- "Arya Flint"
add$father <- "predrik Stark"
add$spouse <- "Rickard Stark"
pred <- rbind(pred, add)


#------------
  

#Adding some more Names

pred[pred$name == "Artos Stark", "mother"] <- "Lorra Royce"
pred[pred$name == "Artos Stark", "father"] <- "Beron Stark"

pred[pred$name == "predwell Stark", "mother"] <- "Alys Karstark"
pred[pred$name == "predwell Stark", "father"] <- "Brandon Stark son of Cregan"

pred[pred$name == "Beron Stark", "mother"] <- "Alys Karstark"
pred[pred$name == "Beron Stark", "father"] <- "Brandon Stark son of Cregan"

pred[pred$name == "Brandon Stark son of Cregan", "mother"] <- "Lynara Stark"
pred[pred$name == "Brandon Stark son of Cregan", "father"] <- "Cregan Stark"

pred[pred$name == "Cregan Stark", "mother"] <- "Gilliane Glover"
pred[pred$name == "Cregan Stark", "father"] <- "Rickon Stark son of Benjen"

pred[pred$name == "Cersei Lannister", "mother"] <- "Joanna Lannister"
pred[pred$name == "Cersei Lannister", "father"] <- "Tywin Lannister"

pred[pred$name == "Jaime Lannister", "mother"] <- "Joanna Lannister"
pred[pred$name == "Jaime Lannister", "father"] <- "Tywin Lannister"

pred[pred$name == "Tyrion Lannister", "mother"] <- "Joanna Lannister"
pred[pred$name == "Tyrion Lannister", "father"] <- "Tywin Lannister"

pred[pred$name == "Joffrey Baratheon", "child_of"] <- "Jaime Lannister"
pred[pred$name == "Myrcella Baratheon", "child_of"] <- "Jaime Lannister"
pred[pred$name == "Tommen Baratheon", "child_of"] <- "Jaime Lannister"

pred[pred$name == "Jonnel Stark", "father"] <- "Cregan Stark"
pred[pred$name == "Jonnel Stark", "mother"] <- "Lynara Stark"

pred[pred$name == "Brendan Stark son of Cregan", "father"] <- "Cregan Stark"
pred[pred$name == "Brendan Stark son of Cregan", "child_of"] <- NA

pred[pred$name == "Eddard Stark", "mother"] <- "Lyarra Stark"
pred[pred$name == "Benjen Stark", "mother"] <- "Lyarra Stark"
pred[pred$name == "Brandon Stark", "mother"] <- "Lyarra Stark"
pred[pred$name == "Lyanna Stark", "mother"] <- "Lyarra Stark"

pred[pred$name == "Edwyle Stark", "mother"] <- "Melantha Blackwood"
pred[pred$name == "Edwyle Stark", "father"] <- "Willam Stark"

pred[pred$name == "Cerenna Lannister", "mother"] <- "Myranda Lefford"
pred[pred$name == "Myrielle Lannister", "mother"] <- "Myranda Lefford"
pred[pred$name == "Daven Lannister", "mother"] <- "Myranda Lefford"

pred[pred$name == "Cerenna Lannister", "father"] <- "Stafford Lannister"
pred[pred$name == "Myrielle Lannister", "father"] <- "Stafford Lannister"
pred[pred$name == "Daven Lannister", "father"] <- "Stafford Lannister"

pred[pred$name == "Joanna Lannister", "father"] <- "Jason Lannister"
pred[pred$name == "Joanna Lannister", "mother"] <- "Marla Prester"

pred[pred$name == "Stafford Lannister", "father"] <- "Jason Lannister"
pred[pred$name == "Stafford Lannister", "mother"] <- "Marla Prester"

pred[pred$name == "Tywin Lannister", "father"] <- "Tytos Lannister"
pred[pred$name == "Kevan Lannister", "father"] <- "Tytos Lannister"
pred[pred$name == "Genna Lannister", "father"] <- "Tytos Lannister"

pred[pred$name == "Lancel Lannister", "father"] <- "Kevan Lannister"
pred[pred$name == "Lancel Lannister", "mother"] <- "Dorna Swyft"

pred[pred$name == "Willem Lannister", "father"] <- "Kevan Lannister"
pred[pred$name == "Willem Lannister", "mother"] <- "Dorna Swyft"

pred[pred$name == "Brandon Stark son of Cregan", "child_of"] <- NA

pred[pred$name == "Lanna Lannister", "father"] <- "Damion Lannister"
pred[pred$name == "Lanna Lannister", "mother"] <- "Shiera Crakehall"

pred[pred$name == "Lucion Lannister", "father"] <- "Damion Lannister"
pred[pred$name == "Lucion Lannister", "mother"] <- "Shiera Crakehall"

pred[pred$name == "Damion Lannister", "father"] <- "Damon Lannister son of Jason"
pred[pred$name == "Damion Lannister", "mother"] <- "Ella Lannister"

pred[pred$name == "Damon Lannister son of Jason", "father"] <- "Jason Lannister"
pred[pred$name == "Damon Lannister son of Jason", "child_of"] <- NA
pred[pred$name == "Damon Lannister son of Jason", "mother"] <- "Alys Stackspear"

pred[pred$name == "Jason Lannister", "father"] <- "Gerold Lannister"
pred[pred$name == "Jason Lannister", "mother"] <- "Rohanne Webber"

pred[pred$name == "Damon Lannister lord", "name"] <- "Damon Lannister"
pred[pred$name == "Tybolt Lannister", "father"] <- "Damon Lannister"
pred[pred$name == "Tybolt Lannister", "mother"] <- "Cerissa Brax"

pred[pred$name == "Gerold Lannister", "father"] <- "Damon Lannister"
pred[pred$name == "Gerold Lannister", "mother"] <- "Cerissa Brax"

pred[pred$name == "Tygett Lannister", "father"] <- "Tytos Lannister"
pred[pred$name == "Tygett Lannister", "mother"] <- "Jeyne Marbrand"
pred[pred$name == "Tywin Lannister", "mother"] <- "Jeyne Marbrand"
pred[pred$name == "Kevan Lannister", "mother"] <- "Jeyne Marbrand"
pred[pred$name == "Genna Lannister", "mother"] <- "Jeyne Marbrand"

pred[pred$name == "Gerion Lannister", "father"] <- "Tytos Lannister"
pred[pred$name == "Gerion Lannister", "mother"] <- "Jeyne Marbrand"

pred[pred$name == "Tyrek Lannister", "father"] <- "Tygett Lannister"
pred[pred$name == "Tyrek Lannister", "mother"] <- "Darlessa Marbrand"

pred[pred$name == "Steffon Baratheon", "father"] <- "Ormund Baratheon"
pred[pred$name == "Steffon Baratheon", "mother"] <- "Rhaelle Targaryen"

pred[pred$name == "Daenerys Targaryen", "father"] <- "Aerys II Targaryen"
pred[pred$name == "Daenerys Targaryen", "mother"] <- "Rhaella Targaryen"

pred[pred$name == "Viserys Targaryen", "father"] <- "Aerys II Targaryen"
pred[pred$name == "Viserys Targaryen", "mother"] <- "Rhaella Targaryen"

pred[pred$name == "Rhaegar Targaryen", "father"] <- "Aerys II Targaryen"
pred[pred$name == "Rhaegar Targaryen", "mother"] <- "Rhaella Targaryen"

pred[pred$name == "Rhaella Targaryen", "father"] <- "Jaehaerys II Targaryen"
pred[pred$name == "Rhaella Targaryen", "mother"] <- "Shaera Targaryen"

pred[pred$name == "Rhaenys Targaryen daughter of Rhaegar", "father"] <- "Rhaegar Targaryen"
pred[pred$name == "Rhaenys Targaryen daughter of Rhaegar", "mother"] <- "Elia Martell"
pred[pred$name == "Rhaenys Targaryen daughter of Rhaegar", "child_of"] <- NA

pred[pred$name == "Aegon Targaryen daughter of Rhaegar", "father"] <- "Rhaegar Targaryen"
pred[pred$name == "Aegon Targaryen daughter of Rhaegar", "mother"] <- "Elia Martell"
pred[pred$name == "Aegon Targaryen daughter of Rhaegar", "child_of"] <- NA

pred[pred$name == "Aegon IV Targaryen", "father"] <- "Aerys II Targaryen"
pred[pred$name == "Aegon IV Targaryen", "mother"] <- "Rhaella Targaryen"

add <- pred[pred$name == "Jaehaerys II Targaryen", ]
add[, "name"] <- "Shaera Targaryen"
pred <- rbind(pred, add)

#------------


pred[pred$name == "Duncan Targaryen", "father"] <- "Aegon V Targaryen"
pred[pred$name == "Duncan Targaryen", "mother"] <- "Betha Blackwood"

pred[pred$name == "Rhaelle Targaryen", "father"] <- "Aegon V Targaryen"
pred[pred$name == "Rhaelle Targaryen", "mother"] <- "Betha Blackwood"

pred[pred$name == "Theodore Tyrell", "father"] <- "Luthor Tyrell son of Moryn"
pred[pred$name == "Theodore Tyrell", "mother"] <- "Elyn Norridge"

pred[pred$name == "Mace Tyrell", "father"] <- "Luthor Tyrell"
pred[pred$name == "Mace Tyrell", "mother"] <- "Olenna Redwyne"

pred[pred$name == "Luthor Tyrell", "father"] <- "Unknown father Tyrell"
pred[pred$name == "Luthor Tyrell", "mother"] <- "Unknown mother Tyrell"

pred[pred$name == "Moryn Tyrell", "father"] <- "Unknown father Tyrell"
pred[pred$name == "Moryn Tyrell", "mother"] <- "Unknown mother Tyrell"

pred[pred$name == "Luthor Tyrell son of Moryn", "father"] <- "Moryn Tyrell"
pred[pred$name == "Luthor Tyrell son of Moryn", "child_of"] <- NA

pred[pred$name == "Garlan Tyrell", "father"] <- "Mace Tyrell"
pred[pred$name == "Garlan Tyrell", "mother"] <- "Alerie Hightower"

pred[pred$name == "Willas Tyrell", "father"] <- "Mace Tyrell"
pred[pred$name == "Willas Tyrell", "mother"] <- "Alerie Hightower"

pred[pred$name == "Loras Tyrell", "father"] <- "Mace Tyrell"
pred[pred$name == "Loras Tyrell", "mother"] <- "Alerie Hightower"

pred[pred$name == "Margaery Tyrell", "father"] <- "Mace Tyrell"
pred[pred$name == "Margaery Tyrell", "mother"] <- "Alerie Hightower"

pred[pred$name == "Mina Tyrell", "father"] <- "Luthor Tyrell"
pred[pred$name == "Mina Tyrell", "mother"] <- "Olenna Redwyne"

pred[pred$name == "Hobber Redwyne", "mother"] <- "Mina Tyrell"
pred[pred$name == "Hobber Redwyne", "father"] <- "Paxter Redwyne"

pred[pred$name == "Horas Redwyne", "mother"] <- "Mina Tyrell"
pred[pred$name == "Horas Redwyne", "father"] <- "Paxter Redwyne"

pred[pred$name == "Olene Tyrell", "mother"] <- "Elyn Norridge"
pred[pred$name == "Olene Tyrell", "father"] <- "Luthor Tyrell son of Moryn"

pred[pred$name == "Medwick Tyrell", "mother"] <- "Elyn Norridge"
pred[pred$name == "Medwick Tyrell", "father"] <- "Luthor Tyrell son of Moryn"

pred[pred$name == "Elinor Tyrell", "mother"] <- "Lia Serry"
pred[pred$name == "Elinor Tyrell", "father"] <- "Theodore Tyrell"

pred[pred$name == "Luthor Tyrell son of Theodore", "mother"] <- "Lia Serry"
pred[pred$name == "Luthor Tyrell son of Theodore", "father"] <- "Theodore Tyrell"
pred[pred$name == "Luthor Tyrell son of Theodore", "child_of"] <- NA

pred[pred$name == "Oberyn Martell", "mother"] <- "Princess of Dorne"
pred[pred$name == "Doran Martell", "mother"] <- "Princess of Dorne"
pred[pred$name == "Mors Martell brother of Doran", "mother"] <- "Princess of Dorne"
pred[pred$name == "Elia Martell", "mother"] <- "Princess of Dorne"

pred[pred$name == "Doran Martell", "house"] <- "House Martell"

pred[pred$name == "Obara Sand", "father"] <- "Oberyn Martell"
pred[pred$name == "Nymeria Sand", "father"] <- "Oberyn Martell"
pred[pred$name == "Tyene Sand", "father"] <- "Oberyn Martell"
pred[pred$name == "Sarella Sand", "father"] <- "Oberyn Martell"

pred[pred$name == "Elia Sand", "father"] <- "Oberyn Martell"
pred[pred$name == "Elia Sand", "mother"] <- "Ellaria Sand"

pred[pred$name == "Obella Sand", "father"] <- "Oberyn Martell"
pred[pred$name == "Obella Sand", "mother"] <- "Ellaria Sand"

pred[pred$name == "Dorea Sand", "father"] <- "Oberyn Martell"
pred[pred$name == "Obella Sand", "mother"] <- "Ellaria Sand"

pred[pred$name == "Loreza Sand", "father"] <- "Oberyn Martell"
pred[pred$name == "Loreza Sand", "mother"] <- "Ellaria Sand"

pred[pred$name == "Aegon Targaryen son of Rhaegar", "father"] <- "Rhaegar Targaryen"
pred[pred$name == "Aegon Targaryen son of Rhaegar", "mother"] <- "Elia Martell"
pred[pred$name == "Aegon Targaryen son of Rhaegar", "child_of"] <- NA

pred[pred$name == "Jon Arryn", "father"] <- "Jasper Arryn"
pred[pred$name == "Alys Arryn", "father"] <- "Jasper Arryn"

pred[pred$name == "Stevron Frey", "father"] <- "Walder Frey"
pred[pred$name == "Stevron Frey", "mother"] <- "Perra Royce"

pred[pred$name == "Emmon Frey", "father"] <- "Walder Frey"
pred[pred$name == "Emmon Frey", "mother"] <- "Perra Royce"

pred[pred$name == "Aenys Frey", "father"] <- "Walder Frey"
pred[pred$name == "Aenys Frey", "mother"] <- "Perra Royce"

pred[pred$name == "Ryman Frey", "father"] <- "Stevron Frey"
pred[pred$name == "Ryman Arryn", "mother"] <- "Corenna Swan"

pred[pred$name == "Edwyn Frey", "father"] <- "Ryman Frey"
pred[pred$name == "Petyr Frey", "father"] <- "Ryman Frey"

pred[pred$name == "Walda Frey", "father"] <- "Edwyn Frey"
pred[pred$name == "Walda Frey", "mother"] <- "Janyce Hunter"

pred[pred$name == "Perra Frey", "father"] <- "Petyr Frey"
pred[pred$name == "Perra Frey", "mother"] <- "Mylenda Caron"

pred[pred$name == "Maegelle Frey", "father"] <- "Stevron Frey"
pred[pred$name == "Maegelle Frey", "mother"] <- "Jeyne Lydden"

pred[pred$name == "Marianne Vance", "father"] <- "Dafyn Vance"
pred[pred$name == "Marianne Vance", "mother"] <- "Maegelle Frey"

pred[pred$name == "Walder Vance", "father"] <- "Dafyn Vance"
pred[pred$name == "Walder Vance", "mother"] <- "Maegelle Frey"

pred[pred$name == "Patrek Vance", "father"] <- "Dafyn Vance"
pred[pred$name == "Patrek Vance", "mother"] <- "Maegelle Frey"

pred[pred$name == "Walton Frey", "father"] <- "Stevron Frey"
pred[pred$name == "Walton Frey", "mother"] <- "Marsella Weynwood"

pred[pred$name == "Steffon Frey", "father"] <- "Walton Frey"
pred[pred$name == "Steffon Frey", "mother"] <- "Deana Hardyng"

pred[pred$name == "Bryan Frey", "father"] <- "Walton Frey"
pred[pred$name == "Bryan Frey", "mother"] <- "Deana Hardyng"

pred[pred$name == "Walda Frey daughter of Walton", "father"] <- "Walton Frey"
pred[pred$name == "Walda Frey daughter of Walton", "mother"] <- "Deana Hardyng"

pred[pred$name == "Harlon Greyjoy", "father"] <- "Quellon Greyjoy"
pred[pred$name == "Harlon Greyjoy", "mother"] <- "Lady of House Stonetree"

pred[pred$name == "Quenton Greyjoy", "father"] <- "Quellon Greyjoy"
pred[pred$name == "Quenton Greyjoy", "mother"] <- "Lady of House Stonetree"

pred[pred$name == "Donel Greyjoy", "father"] <- "Quellon Greyjoy"
pred[pred$name == "Donel Greyjoy", "mother"] <- "Lady of House Stonetree"

pred[pred$name == "predrik Greyjoy", "father"] <- "Balon Greyjoy"
pred[pred$name == "predrik Greyjoy", "mother"] <- "Alannys Harlaw"


#-------

pred[pred$name == "Maron Greyjoy", "father"] <- "Balon Greyjoy"
pred[pred$name == "Maron Greyjoy", "mother"] <- "Alannys Harlaw"

pred[pred$name == "Urrigon Greyjoy", "father"] <- "Quellon Greyjoy"
pred[pred$name == "Urrigon Greyjoy", "mother"] <- "Lady of House Sunderly"

pred[pred$name == "Aeron Greyjoy", "father"] <- "Quellon Greyjoy"
pred[pred$name == "Aeron Greyjoy", "mother"] <- "Lady of House Sunderly"

pred[pred$name == "Robin Greyjoy", "father"] <- "Quellon Greyjoy"
pred[pred$name == "Robin Greyjoy", "mother"] <- "Lady of House Piper"

pred[pred$name == "Ryman Frey", "mother"] <- "Corenna Swann"

pred[pred$name == "Walda Frey daughter of Edwyn", "father"] <- "Edwyn Frey"
pred[pred$name == "Walda Frey daughter of Edwyn", "mother"] <- "Janyce Hunter"

pred[pred$name == "Aegon Frey son of Stevron", "father"] <- "Stevron Frey"
pred[pred$name == "Aegon Frey son of Stevron", "mother"] <- "Jeyne Lydden"

pred[pred$name == "Cleos Frey", "father"] <- "Emmon Frey"
pred[pred$name == "Cleos Frey", "mother"] <- "Genna Lannister"

pred[pred$name == "Tywin Frey", "father"] <- "Cleos Frey"
pred[pred$name == "Tywin Frey", "mother"] <- "Jeyne Darry"

pred[pred$name == "Willem Frey", "father"] <- "Cleos Frey"
pred[pred$name == "Willem Frey", "mother"] <- "Jeyne Darry"

pred[pred$name == "Lyonel Frey", "father"] <- "Emmon Frey"
pred[pred$name == "Lyonel Frey", "mother"] <- "Genna Lannister"

pred[pred$name == "Tion Frey", "father"] <- "Emmon Frey"
pred[pred$name == "Tion Frey", "mother"] <- "Genna Lannister"

pred[pred$name == "Walder Frey son of Emmon", "father"] <- "Emmon Frey"
pred[pred$name == "Walder Frey son of Emmon", "mother"] <- "Genna Lannister"

pred[pred$name == "Amerei Frey", "father"] <- "Merrett Frey"
pred[pred$name == "Amerei Frey", "mother"] <- "Mariya Darry"

pred[pred$name == "Walda Frey daughter of Merrett", "father"] <- "Merrett Frey"
pred[pred$name == "Walda Frey daughter of Merrett", "mother"] <- "Mariya Darry"

pred[pred$name == "Walder Frey son of Merrett", "father"] <- "Merrett Frey"
pred[pred$name == "Walder Frey son of Merrett", "mother"] <- "Mariya Darry"

pred[pred$name == "Marissa Frey", "father"] <- "Merrett Frey"
pred[pred$name == "Marissa Frey", "mother"] <- "Mariya Darry"

pred[pred$name == "Merrett Frey", "father"] <- "Walder Frey"
pred[pred$name == "Merrett Frey", "mother"] <- "Amarei Crakehall"

pred[pred$name == "Roslin Frey", "father"] <- "Walder Frey"
pred[pred$name == "Roslin Frey", "mother"] <- "Bethany Rosby"

pred[pred$name == "Olyvar Frey", "father"] <- "Walder Frey"
pred[pred$name == "Olyvar Frey", "mother"] <- "Bethany Rosby"

pred[pred$name == "Willamen Frey", "father"] <- "Walder Frey"
pred[pred$name == "Willamen Frey", "mother"] <- "Bethany Rosby"

pred[pred$name == "Benfrey Frey", "father"] <- "Walder Frey"
pred[pred$name == "Benfrey Frey", "mother"] <- "Bethany Rosby"

pred[pred$name == "Perwyn Frey", "father"] <- "Walder Frey"
pred[pred$name == "Perwyn Frey", "mother"] <- "Bethany Rosby"

pred[, c(6, 12:13, 15, 34)] %>% arrange(name)
pred[grep("Perwyn", pred$name), c(6, 12:13, 15, 34)] %>% arrange(name)
add <- pred[pred$name == "Willam Stark", ]
add[, "spouse"] <- "Lyanna Glover"
pred <- rbind(pred, add)

add <- pred[pred$name == "Sansa Stark", ]
add[, "spouse"] <- "Ramsay Snow"
pred <- rbind(pred, add)

add <- pred[pred$name == "Cregan Stark", ]
add[, "spouse"] <- "Lynara Stark"
pred <- rbind(pred, add)

pred[pred$name == "Steffon Baratheon", "spouse"] <- "Cassana Baratheon"
pred[pred$name == "Tommen Baratheon", "spouse"] <- "Margaery Tyrell"
pred[pred$name == "Joffrey Baratheon", "spouse"] <- "Margaery Tyrell"

pred[pred$name == "Jason Lannister", "spouse"] <- "Alys Stackspear"

add <- pred[pred$name == "Jason Lannister", ]
add[, "spouse"] <- "Marla Prester"
pred <- rbind(pred, add)

add <- pred[pred$name == "Gerold Lannister", ]
add[, "spouse"] <- "Rohanne Webber"
pred <- rbind(pred, add)

pred[pred$name == "Aerys II Targaryen", "spouse"] <- "Rhaella Targaryen"

add <- pred[pred$name == "Daenerys Targaryen", ]
add[, "spouse"] <- "Hizdahr zo Loraq"
pred <- rbind(pred, add)

pred[pred$name == "Hizdahr zo Loraq", "spouse"] <- "Daenerys Targaryen"

add <- pred[pred$name == "Margaery Tyrell", ]
add[, "spouse"] <- "Joffrey Baratheon"
pred <- rbind(pred, add)

add <- pred[pred$name == "Margaery Tyrell", ]
add[, "spouse"] <- "Tommen Baratheon"
pred <- rbind(pred, add)

pred[pred$name == "Elyn Norridge", "spouse"] <- "Luthor Tyrell son of Moryn"

```


Adding More Rows

```{r}
add <- pred[pred$name == "Jon Arryn", ]
add[, "spouse"] <- "Lysa Arryn"
pred <- rbind(pred, add)

add <- pred[pred$name == "Jon Arryn", ]
add[, "spouse"] <- "Rowena Arryn"
pred <- rbind(pred, add)

add <- pred[pred$name == "Stevron Frey", ]
add[, "spouse"] <- "Marsella Waynwood"
pred <- rbind(pred, add)

add <- pred[pred$name == "Stevron Frey", ]
add[, "spouse"] <- "Jeyne Lydden"
pred <- rbind(pred, add)

add <- pred[pred$name == "Lysa Arryn", ]
add[, "spouse"] <- "Petyr Baelish"
pred <- rbind(pred, add)

pred[pred$name == "Quellon Greyjoy", "spouse"] <- "Lady of House Stonetree"

add <- pred[pred$name == "Quellon Greyjoy", ]
add[, "spouse"] <- "Lady of House Sunderly"
pred <- rbind(pred, add)

add <- pred[pred$name == "Quellon Greyjoy", ]
add[, "spouse"] <- "Lady of House Piper"
pred <- rbind(pred, add)

pred[, c(6, 15:16)] %>% arrange(name)
pred[grep("Bethany", pred$name), c(6, 15:16)] %>% arrange(name)

```


####Generating more New Dataframes


```{r}
#contains Mothers
pred_2a <- pred[, c(6, 12)] %>%
  na.omit()

#Contains Fathers
pred_2b <- pred[, c(6, 13)] %>%
  na.omit()

#Child of
pred_3 <- pred[, c(6, 34)] %>%
  na.omit()

#Spouse Dataset
pred_4 <- pred[, c(6, 16)] %>%
  na.omit()


```



####Generating the first Network Dataset

```{r}

net1 <- data.frame(source = c(pred_2a$mother, pred_2b$father, pred_3$child_of, pred_4$name),
                  target = c(pred_2a$name, pred_2b$name, pred_3$name, pred_4$spouse),
                  type = c(rep("mother", nrow(pred_2a)), rep("father", nrow(pred_2b)), rep("father/mother", nrow(pred_3)), rep("spouse", nrow(pred_4))))

head(net1)


```

-----------------



##Scraping GOT Data


```{r,message=FALSE,warning=FALSE}
require(rvest)


#Scraping all the main characters fro wikipedia
main.page <- read_html("https://en.wikipedia.org/wiki/List_of_Game_of_Thrones_characters")

names <- main.page %>% # feed `main.page` to the next step  
  html_nodes(xpath='//*[@id="mw-content-text"]/div/table[2]') %>%
  .[[1]] %>%
  html_table(fill=T)

#removing irrelevant columns
for(i in 1:7)
{
  names$Appearances<-NULL
}

#renaming the columns
names(names)<-c("actor","name")
names$actor<-NULL
names<-names[names$name=="Character",]#removing a irrelevant row

#final data frame with major character names
df_final_major <- data.frame(names)


```


###Scraping the list of Minor and Supporting characters

```{r}
main.page <- read_html("https://en.wikipedia.org/wiki/List_of_Game_of_Thrones_characters")

#List of Minor actors
names <- main.page %>%  
  html_nodes(xpath='//*[@id="mw-content-text"]/div/table[3]') %>%
  .[[1]] %>%
  html_table(fill=T)


for(i in 1:7)
{
  names$Appearances<-NULL
}

#renaming the columns
names(names)<-c("actor","name")
names$actor<-NULL
names<-names[!names$name=="Character",]#removing a irrelevant row


df_final_minor <-data.frame(names)

```

###Final Data frame
```{r}
df_final <- rbind(df_final_major,
                  df_final_minor)

names(df_final)<-c("name")

```
This data frame consists of all the characters in GOT i.e all supporting and Major characters.

Saving the data frame.
```{r}
save(df_final, file = "df_final.RData")

load("df_final.RData")



```

```{r}

net <- rbind(net1)
net$source <- as.character(net$source)
net$target <- as.character(net$target)
net$type <- as.character(net$type)

net[net == "Cassana Estermont"] <- "Cassana Baratheon"
net[net == "Catelyn Tully"] <- "Catelyn Stark"
net[net == "Ramsay Snow"] <- "Ramsay Bolton"

net <- net[!duplicated(net), ]
net <- rbind(net, c("Talisa Stark", "Robb Stark", "spouse"))
net[net$target == "Aegon IV Targaryen" & net$type == "mother", "source"] <- "Viserys II Targaryen"
net[net$target == "Aegon IV Targaryen" & net$type == "father", "source"] <- "Larra Rogare"
net[net$target == "Maron Martell", "target"] <- "Maron Martell I"

#----------

pred$name <- as.character(pred$name)
characters <- data.frame(name = unique(c(as.character(net$source), as.character(net$target)))) %>%
  mutate(name = as.character(name)) %>%
  left_join(pred[, c(6, 8, 9, 15, 32:34)], by = "name")

characters[characters == ""] <- NA
#assigning 0 as NA value
characters$popularity[is.na(characters$popularity)] <- 0
#removing duplicate characters
characters <- characters[!duplicated(characters), ]

```

