---
title: 'Network Analysis of Game of Thrones '
output:
  html_document: default
  html_notebook: default
---
```{r, include=FALSE}
require(dplyr)
characters <- data.frame(name=unique(c(as.character(net$source), as.character(net$target)))) %>%
  mutate(name = as.character(name)) %>%
  left_join(pred[, c(6, 8, 9, 15, 32:34)], by = "name")

characters[characters == ""] <- NA
#assigning 0 as NA value
characters$popularity[is.na(characters$popularity)] <- 0
#removing duplicate characters
characters <- characters[!duplicated(characters), ]

```


```{r, include=FALSE}

characters[characters$name == "Tya Lannister", "male"] <- 0
characters[grep("Aegon", characters$name), "male"] <- 1
characters[grep("Aerys", characters$name), "male"] <- 1
characters[grep("Baelon", characters$name), "male"] <- 1
  
for (i in 1:nrow(characters)) {
  
    name <- characters[i, "name"]
    value <- ifelse(name %in% net$source & any(net[net$source == name, "type"] == "mother"), 0, 
                    ifelse(name %in% net$source & any(net[net$source == name, "type"] == "father"), 1, characters[i, "male"]))
    
    characters[i, "male"] <- value
}

#making a Boolean column with male as 1 otherwise 0
characters[characters$name == "Ramsay Bolton", "male"] <- 1
characters[characters$name == "Arya Stark", "male"] <- 0
characters[characters$name == "Sansa Stark", "male"] <- 0
characters[characters$name == "Robb Stark", "male"] <- 1
characters[characters$name == "Rickon Stark", "male"] <- 1
characters[characters$name == "Bran Stark", "male"] <- 1
characters[characters$name == "Jon Snow", "male"] <- 1

for (i in 1:nrow(characters)) {
  value <- characters[i, "male"]
  
  if (is.na(value)) {
    name <- characters[i, "name"]
        type <- net[which(net$source == name | net$target == name), "type"]
        
        if (any(type == "spouse")) {
          net2 <- net[which(net$source == name | net$target == name), ] %>%
            filter(type == "spouse")
          
          if (nrow(net2) > 1) {
            sp <- c(net2[, "source"], net2[, "target"])
            sp <- sp[which(sp != name)]
            
            for (j in length(sp)) {
              spouse <- sp[j]
              value[j] <- ifelse(characters[characters$name == spouse, "male"] == 1, 0, 
                          ifelse(characters[characters$name == spouse, "male"] == 0, 1, NA))
            }
            
            value <- na.omit(value)[1]
          } else {
            sp1 <- net2[, "source"]
            sp2 <- net2[, "target"]
            
            spouse <- ifelse(sp1 == name, sp2, sp1)
            value <- ifelse(characters[characters$name == spouse, "male"] == 1, 0, 
                            ifelse(characters[characters$name == spouse, "male"] == 0, 1, NA))
          }
          
          characters[i, "male"] <- value
        }
  }
  
}





#Adding houses columns to the characters dataframe
#------------


for (i in 1:nrow(characters)) {
  
  if (!is.na(characters[i, "male"])) {
    
    if (characters[i, "male"] == 1 & is.na(characters[i, "house"])) {
    
      name <- gsub(" son of .*", "", characters[i, "name"])
      characters[i, "house"] <- paste("House", gsub("(.* )(.*$)", "\\2", name))
    }
    
    if (characters[i, "male"] == 0) {
      
      name <- characters[i, "name"]
      father <- net[which(net$target == name & net$type == "father"), ]
      
      if (nrow(father) > 0) {
        
        characters[i, "house"] <- paste("House", gsub("(.* )(.*$)", "\\2", father$source))
      } else {
        
        characters[i, "house"] <- paste("House", gsub("(.* )(.*$)", "\\2", characters[i, "name"]))
      }
  }
  } else {
    
    characters[i, "house"] <- paste("House", gsub("(.* )(.*$)", "\\2", characters[i, "name"]))
  }
}

characters[grep("Baratheon", characters$house), "house"] <- "House Baratheon"
characters[grep("Bolton", characters$house), "house"] <- "House Bolton"
characters[grep("Fossoway", characters$house), "house"] <- "House Fossoway"
characters[grep("Frey", characters$house), "house"] <- "House Frey"
characters[grep("Lannister", characters$house), "house"] <- "House Lannister"
characters[grep("Tyrell", characters$house), "house"] <- "House Tyrell"
characters[grep("Stark", characters$house), "house"] <- "House Stark"
characters[grep("Targaryen", characters$house), "house"] <- "House Targaryen"

characters[characters$name == "Rickon Stark son of Benjen", "house"] <- "House Stark"
characters[characters$name == "Drogo", "house"] <- "Dothraki"

characters$house2 <- ifelse(characters$house %in% c("House Targaryen", "House Stark", "House Tully", "House Lannister", "House Baratheon", "House Tyrell", "House Martell", "House Frey", "House Greyjoy"), characters$house, NA)

```


```{r, include=FALSE}
net[net$source == "Rhaegar Targaryen" & net$target == "Aegon Targaryen son of Rhaegar", "type"] <- "father"

characters[characters$name == "Aegon II", "name"] <- "Aegon II Targaryen"
characters[characters$name == "Aegon II Targaryen", "house"] <- "House Targaryen"
characters[characters$name == "Aegon Targaryen son of Jaehaerys I", "house"] <- "House Targaryen"
characters[characters$name == "Marsella Weynwood", "name"] <- "Marsella Waynwood"


#adding color to the Network edges
library(RColorBrewer)

#adding colors to the types i.e father,mother,spouse i.e relationships
colors_edges <- with(net,
                     data.frame(type = levels(as.factor(type)),
                                color = I(brewer.pal(nlevels(as.factor(type)), name = 'Dark2'))))

#Joining net and color_edges df by type
net <- left_join(net, colors_edges, by = "type")

#------------
#coloring the nodes on the basis of house

color_vertices <- with(characters,
                       data.frame(house2 = levels(as.factor(house2)),
                                  color = I(brewer.pal(nlevels(as.factor(house2)), name = 'Set1'))))

#joining the colored vertices with characters dataframe
characters <- left_join(characters, color_vertices, by = "house2")

#Shapes of the Gender
characters$shape <- ifelse(characters$male == 1, "square",
                                 ifelse(characters$male == 0, "circle", "triangle"))

characters$shape[is.na(characters$shape)] <- "none"

```


###This Article will now consist of the plotting Directed Acyclic Graphs of relationships 

The previous article consisted of the Data Processing,data scraping and preparing the data to be used in making Network DAGs.

```{r,warning=FALSE,message=FALSE}
require(tidyverse)
require(igraph)

```
```{r}
#making a new data frame consisting of all people in House Frey
characters_Frey <- characters %>%
  filter(name %in% c("Emmon Frey", "Cleos Frey", "Tywin Frey", "Willem Frey", "Lyonel Frey", "Tion Frey", "Walder Frey son of Emmon", "Amerei Frey", "Lancel Lannister", "Merrett Frey", "Walda Frey daughter of Merrett", "Walder Frey son of Merrett", "Marissa Frey", "Roslin Frey", "Olyvar Frey", "Willamen Frey", "Benfrey Frey", "Perwyn Frey"))

net_Frey <- net %>%
  filter(source %in% characters_Frey$name | target %in% characters_Frey$name)

#adding line types and arrows i.e edges
net_Frey$lty <- "solid"
net_Frey$arrow <- ifelse(net_Frey$type == "spouse", 3, 2)

net_Frey <- net_Frey[net_Frey$type != "father/mother", ]
net_Frey <- rbind(net_Frey,
                  c("Perra Royce", "Walder Frey", "spouse", "#E7298A", "solid", 3),
                  c("Amarei Crakehall", "Walder Frey", "spouse", "#E7298A", "solid", 3),
                  c("Bethany Rosby", "Walder Frey", "spouse", "#E7298A", "solid", 3))

characters_Frey <- characters %>%
  filter(name %in% net_Frey$source | name %in% net_Frey$target) %>%
  arrange(name)


#?graph_from_data_frame to search on this function
graph_Frey <- graph_from_data_frame(net_Frey, directed = TRUE, vertices = characters_Frey)


```

Now we will generate Directed Acyclic Graphs using igraph package

```{r,out.height=15,out.width=20}
#using pdf to generate pdf graphics
pdf("family_frey_tree.pdf", width = 20, height = 15)
#Plotting the DAG for Frey family
plot(graph_Frey,
     layout = layout_with_lgl,
     vertex.label = gsub(" ", "\n", V(graph_Frey)$name),
     vertex.shape = V(graph_Frey)$shape,
     vertex.color = V(graph_Frey)$color, 
     vertex.size = (V(graph_Frey)$popularity + 0.5) * 5, 
     vertex.frame.color = "gray", 
     vertex.label.color = "black", 
     vertex.label.cex = 0.8,
     edge.arrow.mode = E(graph_Frey)$arrow,
     edge.arrow.size = 0.5,
     edge.color = E(graph_Frey)$color,
     edge.lty = E(graph_Frey)$lty)

legend("topleft", legend = c(as.character(color_vertices$house), as.character(colors_edges$type)), pch = 19,
       col = c(color_vertices$color, colors_edges$color), pt.cex = 2, cex = 1, bty = "n", ncol = 1)


```

---------------


###House Stark Tree

```{r}
characters_Stark <- characters %>%
  filter(house == "House Stark")

net_Stark <- net %>%
  filter(source %in% characters_Stark$name | target %in% characters_Stark$name)

net_Stark <- net_Stark[net_Stark$source != "Unnamed mother", ]

net_Stark$lty <- ifelse(net_Stark$source == "Lyanna Stark" & net_Stark$target == "Jon Snow", "dotted", "solid")
net_Stark$lty <- ifelse(net_Stark$source == "Sansa Stark" & net_Stark$target == "Ramsay Bolton", "dotted", net_Stark$lty)
net_Stark$lty <- ifelse(net_Stark$source == "Rhaegar Targaryen" & net_Stark$target == "Jon Snow", "dotted", net_Stark$lty)
net_Stark$lty <- ifelse(net_Stark$source == "Talisa Stark" & net_Stark$target == "Robb Stark", "dotted", net_Stark$lty)

net_Stark$arrow <- ifelse(net_Stark$type == "spouse", 3, 2)

characters_Stark <- characters %>%
  filter(name %in% net_Stark$source | name %in% net_Stark$target) %>%
  arrange(name)

graph_Stark <- graph_from_data_frame(net_Stark, directed = TRUE, vertices = characters_Stark)


```

Stark Family Tree 
```{r}
pdf("family_tree_Stark.pdf", width = 20, height = 15)
plot(graph_Stark,
     layout = layout_with_lgl,
     vertex.label = gsub(" ", "\n", V(graph_Stark)$name),
     vertex.shape = V(graph_Stark)$shape,
     vertex.color = V(graph_Stark)$color, 
     vertex.size = (V(graph_Stark)$popularity + 0.5) * 5, 
     vertex.frame.color = "gray", 
     vertex.label.color = "black", 
     vertex.label.cex = 0.8,
     edge.arrow.mode = E(graph_Stark)$arrow,
     edge.arrow.size = 0.5,
     edge.color = E(graph_Stark)$color,
     edge.lty = E(graph_Stark)$lty)
legend("topleft", legend = c(as.character(color_vertices$house), as.character(colors_edges$type)), pch = 19,
       col = c(color_vertices$color, colors_edges$color), pt.cex = 2, cex = 1, bty = "n", ncol = 1)


```

---------------


###Lannister Family Tree

```{r}
characters_Lannister <- characters %>%
  filter(house == "House Lannister") %>%
  filter(!name %in% c("Margot Lannister", "Tya Lannister"))

net_Lannister <- net %>%
  filter(source %in% characters_Lannister$name | target %in% characters_Lannister$name)

net_Lannister$lty <- ifelse(net_Lannister$source == "Jaime Lannister" & net_Lannister$type == "father/mother", "dotted", "solid")
net_Lannister$type <- ifelse(net_Lannister$source == "Jaime Lannister" & net_Lannister$type == "father/mother", "father", net_Lannister$type)
net_Lannister[net_Lannister$source == "Jaime Lannister" & net_Lannister$type == "father", "color"] <- "#1B9E77"

net_Lannister$arrow <- ifelse(net_Lannister$type == "spouse", 3, 2)

characters_Lannister <- characters %>%
  filter(name %in% net_Lannister$source | name %in% net_Lannister$target) %>%
  arrange(name)

graph_Lannister <- graph_from_data_frame(net_Lannister, directed = TRUE, vertices = characters_Lannister)


```

Plotting the Graph
```{r}
pdf("family_tree_Lannister.pdf", width = 20, height = 15)
plot(graph_Lannister,
     layout = layout_with_lgl,
     vertex.label = gsub(" ", "\n", V(graph_Lannister)$name),
     vertex.shape = V(graph_Lannister)$shape,
     vertex.color = V(graph_Lannister)$color, 
     vertex.size = (V(graph_Lannister)$popularity + 0.5) * 5, 
     vertex.frame.color = "gray", 
     vertex.label.color = "black", 
     vertex.label.cex = 0.8,
     edge.arrow.mode = E(graph_Lannister)$arrow,
     edge.arrow.size = 0.5,
     edge.color = E(graph_Lannister)$color,
     edge.lty = E(graph_Lannister)$lty)
legend("topleft", legend = c(as.character(color_vertices$house), as.character(colors_edges$type)), pch = 19,
       col = c(color_vertices$color, colors_edges$color), pt.cex = 2, cex = 1, bty = "n", ncol = 1)


```

-----------

###Baratheon House
```{r}
characters_Baratheon <- characters %>%
  filter(house == "House Baratheon") %>%
  filter(!name %in% c("Orys Baratheon", "Gowen Baratheon"))

net_Baratheon <- net %>%
  filter(source %in% characters_Baratheon$name | target %in% characters_Baratheon$name)

net_Baratheon$lty <- ifelse(net_Baratheon$source == "Jaime Lannister" & net_Baratheon$type == "father/mother", "dotted", "solid")
net_Baratheon$type <- ifelse(net_Baratheon$source == "Jaime Lannister" & net_Baratheon$type == "father/mother", "father", net_Baratheon$type)
net_Baratheon[net_Baratheon$source == "Jaime Lannister" & net_Baratheon$type == "father", "color"] <- "#1B9E77"

net_Baratheon$arrow <- ifelse(net_Baratheon$type == "spouse", 3, 2)

characters_Baratheon <- characters %>%
  filter(name %in% net_Baratheon$source | name %in% net_Baratheon$target) %>%
  arrange(name)

graph_Baratheon <- graph_from_data_frame(net_Baratheon, directed = TRUE, vertices = characters_Baratheon)

```



---------------------


 
###House Targaryen 

```{r}
characters_Targaryen <- characters %>%
  #filter(house == "House Targaryen")
  filter(name %in% c("Daenerys Targaryen", "Rhaegar Targaryen", "Viserys Targaryen", "Aerys II Targaryen", "Jaehaerys II Targaryen", "Aegon V Targaryen", "Duncan Targaryen", "Rhaelle Targaryen"))

net_Targaryen <- net %>%
  filter(source %in% characters_Targaryen$name | target %in% characters_Targaryen$name)

net_Targaryen$lty <- ifelse(net_Targaryen$source == "Maron Martell" & net_Targaryen$target == "Daenerys Targaryen", "dotted", "solid")
net_Targaryen$lty <- ifelse(net_Targaryen$source == "Rhaegar Targaryen" & net_Targaryen$target == "Jon Snow", "dotted", net_Targaryen$lty)
net_Targaryen$arrow <- ifelse(net_Targaryen$type == "spouse", 3, 2)

characters_Targaryen <- characters %>%
  filter(name %in% net_Targaryen$source | name %in% net_Targaryen$target) %>%
  arrange(name)

graph_Targaryen <- graph_from_data_frame(net_Targaryen, directed = TRUE, vertices = characters_Targaryen)

```


-----------------

###House Tyrell

```{r}
characters_Tyrell <- characters %>%
  #filter(house == "House Tyrell")
  filter(name %in% c("Luthor Tyrell", "Mace Tyrell", "Garlan Tyrell", "Margaery Tyrell", "Loras Tyrell", "Willas Tyrell", "Mina Tyrell", "Horas Redwyne", "Hobber Redwyne", "Moryn Tyrell", "Luthor Tyrell son of Moryn", "Theodore Tyrell", "Luthor Tyrell son of Theodore", "Elinor Tyrell", "Olene Tyrell", "Medwick Tyrell"))

net_Tyrell <- net %>%
  filter(source %in% characters_Tyrell$name | target %in% characters_Tyrell$name)

net_Tyrell$lty <- "solid"
net_Tyrell$arrow <- ifelse(net_Tyrell$type == "spouse", 3, 2)

characters_Tyrell <- characters %>%
  filter(name %in% net_Tyrell$source | name %in% net_Tyrell$target) %>%
  arrange(name)

graph_Tyrell <- graph_from_data_frame(net_Tyrell, directed = TRUE, vertices = characters_Tyrell)

```


---------------


###Martell House

```{r}
characters_Martell <- characters %>%
  filter(house == "House Martell")

characters_Martell <- characters_Martell[characters_Martell$name != "Mors Martell", ]
characters_Martell <- characters_Martell[characters_Martell$name != "Maron Martell", ]
characters_Martell <- characters_Martell[characters_Martell$name != "Mariah Martell", ]

net_Martell <- net %>%
  filter(source %in% characters_Martell$name | target %in% characters_Martell$name)

net_Martell$lty <- "solid"
net_Martell$arrow <- ifelse(net_Martell$type == "spouse", 3, 2)

characters_Martell <- characters %>%
  filter(name %in% net_Martell$source | name %in% net_Martell$target) %>%
  arrange(name)

graph_Martell <- graph_from_data_frame(net_Martell, directed = TRUE, vertices = characters_Martell)

```

----------------

###Tully House


```{r}
characters_Tully <- characters %>%
  filter(house == "House Tully")

net_Tully <- net %>%
  filter(source %in% characters_Tully$name | target %in% characters_Tully$name)

net_Tully <- net_Tully[-which(net_Tully$source == "Edmure Tully" & net_Tully$type == "father"), ]
net_Tully <- net_Tully[-which(net_Tully$source == "Roslin Tully"), ]

net_Tully$lty <- "solid"
net_Tully$arrow <- ifelse(net_Tully$type == "spouse", 3, 2)

characters_Tully <- characters %>%
  filter(name %in% net_Tully$source | name %in% net_Tully$target) %>%
  arrange(name)

graph_Tully <- graph_from_data_frame(net_Tully, directed = TRUE, vertices = characters_Tully)

```




----------------




###Arryn House

```{r}
characters_Arryn <- characters %>%
  filter(house == "House Arryn")

characters_Arryn <- characters_Arryn[characters_Arryn$name != "Aemma Arryn", ]
characters_Arryn <- characters_Arryn[characters_Arryn$name != "Rodrik Arryn", ]

net_Arryn <- net %>%
  filter(source %in% characters_Arryn$name | target %in% characters_Arryn$name)

net_Arryn <- net_Arryn[-which(net_Arryn$target == "Alys Arryn" & net_Arryn$source == "Rhaegel Targaryen"), ]

net_Arryn$lty <- "solid"
net_Arryn$arrow <- ifelse(net_Arryn$type == "spouse", 3, 2)

characters_Arryn <- characters %>%
  filter(name %in% net_Arryn$source | name %in% net_Arryn$target) %>%
  arrange(name)

graph_Arryn <- graph_from_data_frame(net_Arryn, directed = TRUE, vertices = characters_Arryn)


```

-

-----------


###Greyjoy House

```{r}
characters_Greyjoy <- characters %>%
  filter(house == "House Greyjoy")

net_Greyjoy <- net %>%
  filter(source %in% characters_Greyjoy$name | target %in% characters_Greyjoy$name)

net_Greyjoy$lty <- ifelse(net_Greyjoy$target == "Erik Ironmaker" | net_Greyjoy$source == "Erik Ironmaker", "dotted", "solid")
net_Greyjoy$arrow <- ifelse(net_Greyjoy$type == "spouse", 3, 2)

characters_Greyjoy <- characters %>%
  filter(name %in% net_Greyjoy$source | name %in% net_Greyjoy$target) %>%
  arrange(name)

characters_Greyjoy[characters_Greyjoy$name == "Asha Greyjoy", "name"] <- "Asha (Yara) Greyjoy"
net_Greyjoy[net_Greyjoy == "Asha Greyjoy"] <- "Asha (Yara) Greyjoy"

graph_Greyjoy <- graph_from_data_frame(net_Greyjoy, directed = TRUE, vertices = characters_Greyjoy)


```



-----------------


##Now Plotting a Big Graph with all the families 


Making a Big data frame with all families and Houses Information
```{r,warning=F,message=FALSE}
union_edges <- rbind(net_Arryn, 
                     net_Baratheon,
                     net_Frey,
                     net_Greyjoy,
                     net_Lannister,
                     net_Martell,
                     net_Stark,
                     net_Targaryen,
                     net_Tully,
                     net_Tyrell) %>%
  .[!duplicated(.), ]

union_edges <- rbind(union_edges,
                     c("Roose Bolton", "Ramsay Bolton", "father",	"#1B9E77", "solid",	2))

union_edges1 <- union_edges[union_edges$type == "spouse", ]
union_edges1$target <- union_edges[union_edges$type == "spouse", "source"]
union_edges1$source <- union_edges[union_edges$type == "spouse", "target"]

union_edges2 <- rbind(union_edges[union_edges$type != "spouse", ],
                      union_edges[union_edges$type == "spouse", ],
                      union_edges1)

union_edges <- union_edges2 %>%
  .[!duplicated(.), ]

union_edges <- union_edges[, -ncol(union_edges)]

union_characters <- rbind(characters_Arryn, 
                          characters_Baratheon,
                          characters_Frey,
                          characters_Greyjoy,
                          characters_Lannister,
                          characters_Martell,
                          characters_Stark,
                          characters_Targaryen,
                          characters_Tully,
                          characters_Tyrell) %>%
  .[!duplicated(.), ] 

#removing 6 and 7 columns
union_characters <- union_characters[, -c(6, 7)]


#Saving the Data
save(union_edges, file = "union_edges.RData")
save(union_characters, file = "union_characters.RData")


union_graph <- graph_from_data_frame(union_edges, directed = TRUE, vertices = union_characters)


layout <- layout_with_fr(union_graph)
```

For Plotting the legend

```{r}
color_vertices %>%
  group_by(house, color) %>%
  summarise(n = n()) %>%
  filter(!is.na(color))

colors_edges %>%
  group_by(type, color) %>%
  summarise(n = n()) %>%
  filter(!is.na(color))

```


------------


###Now Plotting the GOT family ties


```{r}
require(statnet)
require(igraph)
load("union_edges.RData")
load("union_characters.RData")


#Plotting the GOT family ties
pdf("got_family_ties.pdf",height=15,width=25)
plot(union_graph,
     layout = layout,
     vertex.label = gsub(" ", "\n", V(union_graph)$name),
     vertex.shape = V(union_graph)$shape,
     vertex.color = V(union_graph)$color, 
     vertex.size = (V(union_graph)$popularity + 0.5) * 5, 
     vertex.frame.color = "gray", 
     vertex.label.color = "black", 
     vertex.label.cex = 0.8,
     edge.arrow.size = 0.5,
     edge.color = E(union_graph)$color,
     edge.lty = E(union_graph)$lty)
legend("topleft", legend = c(NA, "Node color:", as.character(color_vertices$house), NA, "Edge color:", as.character(colors_edges$type)), pch = 19,
       col = c(NA, NA, color_vertices$color, NA, NA, colors_edges$color), pt.cex = 5, cex = 2, bty = "n", ncol = 1,
       title = "") 
legend("topleft", legend = "", cex = 4, bty = "n", ncol = 1,
       title = "Game of Thrones Family Ties")



```
Node color shows the major houses, node size the character’s popularity and node shape their gender (square for male, circle for female). Edge color shows interaction type.

As we can see, even with only a subset of characters from the Game of Thrones world, the network is already quite big. You can click on the image to open the pdf and zoom into specific parts of the plot and read the node labels/character names.


What we can see right away is that there are only limited connections between houses and that the Greyjoys are the only house that has no ties to any of the others.







```{r}
union_graph_undir <- as.undirected(union_graph, mode = "collapse")

```


------------------




###Centrality

Centrality describes the number of edges that are in- or outgoing to/from nodes. High centrality networks have few nodes with many connections, low centrality networks have many nodes with similar numbers of edges.

For the whole network, we can calculate centrality by degree 
```{r}
centr_degree(union_graph_undir, mode = "total")$centralization

centr_clo(union_graph_undir, mode = "total")$centralization


centr_eigen(union_graph_undir, directed = FALSE)$centralization


```

---------------



###Node degree


Node degree or degree centrality describes how central a node is in the network (i.e. how many in- and outgoing edges it has or to how many other nodes it is directly connected via one edge).


“The degree of a vertex is its most basic structural property, the number of its adjacent edges.” From the help pages of degree()

We can calculate the number of out- or ingoing edges of each node, or – as I am doing here – the sum of both.


```{r}

```

